InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-14 paper.tex
Update paper.tex
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

Fig. \ref{stable_diffusion} shows how the different processors and their combinations effect an image generated by the stable diffusion generator. The bars are structured in packs of three where the most left one represents the nahrawy evaluator, the middle one is resnet18 and on the right is the umm-maybe evaluator respectively. The different colors represent the different outputs. Black symbolizes that the image before and after processing was detected as AI-generated. Grey shows that both are detected to be human made, whereas for red the process did the exact opposite of what it should do and fool the detector in a way that after processing it is seen as AI-generated whereas before as human made. Lastly the green bar does exactly what is desired, so it pictures AI-generated content, where the executed augmentation lead to the detector guessing it was human-made. \\
It can be seen in fig. \ref{fig:stable_diffusion}, that only the nahrawy evaluator has a little bit of red in it but also it is the only one with the output of 'human-human'. Compared to the dall-E generator in fig. \ref{fig:dallE} the amount of green is relatively low. There are also other differences as here only umm-maybe achieved 'human-ai' but also 'human-human'. 
It is visible that the gaussian noise image processor as well as the salt-and-pepper one are the best processors. This can be seen as they alone achieve a great result as well as their combinations with other ones. It is also worth mentioning that these result are only achieved when using the nahrawy evaluator. Whereas resnet18 which can be seen in both figures has only the output of 'ai-ai'.

>>>>

Fig. \ref{stable_diffusion} shows how the different processors and their combinations effect an image generated by the stable diffusion generator. The bars are structured in packs of three where the most left one represents the nahrawy evaluator, the middle one is resnet18 and on the right is the umm-maybe evaluator respectively. The different colors represent the different outputs. Black symbolizes that the image before and after processing was detected as AI-generated. Grey shows that both are detected to be human made, whereas for red the process did the exact opposite of what it should do and fool the detector in a way that after processing it is seen as AI-generated whereas before as human made. Lastly the green bar does exactly what is desired, so it pictures AI-generated content, where the executed augmentation lead to the detector guessing it was human-made. \\
The data depicted in fig. \ref{fig:stable_diffusion} shows, that only the nahrawy evaluator fooled the detector the wrong way round, but it is also the only one with the output of 'human-human'. Compared to the Dall-E generator in fig. \ref{fig:dallE} the amount of right tricking is relatively low. There are also other differences as here only umm-maybe achieved 'human-ai' but also 'human-human'. 
It is visible that the gaussian noise image processor as well as the salt-and-pepper one are the best processors. This can be seen as they alone achieve a great result as well as their combinations with other ones. It is also worth mentioning that these result are only achieved when using the nahrawy evaluator. Whereas resnet18 which can be seen in both figures has only the output of 'ai-ai'.
